Supporting Information

### 2021-09-01 paper/paper.Rmd
doublespaced
formatting minor
final revs before submission2

---
title: "Modeling and leveraging intuitive theories to improve vaccine attitudes"
author: "Derek Powell, Kara Weisman, and Ellen M. Markman"
output: pdf_document
bibliography: "../supplement/references.bib"
csl: "../supplement/pnas.csl"
---

@@

# Abstract

@@

@@

\newpage
# References

>>>>

---
title: "Modeling and leveraging intuitive theories to improve vaccine attitudes"
author: 
  - Derek Powell^[Arizona State University, dmpowell@asu.edu]
  - Kara Weisman^[University of California, Riverside]
  - Ellen M. Markman^[Stanford University]
output:
  pdf_document:
    keep_tex: true
bibliography: "../supplement/references.bib"
csl: "../supplement/science.csl"
header-includes:
    - \usepackage{setspace}\doublespacing
---

@@

## One sentence summary

We developed a cognitive model of the intuitive theory surrounding vaccination decisions capable of predicting how people's beliefs about vaccination would be revised in light of evidence and real-world events.

## Abstract

@@

# Main text

@@

\newpage
\singlespacing
# References

### 2021-09-01 supplement/supplement-main.Rmd
final revs before submission2

---
title: "Supporting Information"
subtitle: "Modeling and leveraging intuitive theories to improve vaccine attitudes"
author: "Derek Powell, Kara Weisman, and Ellen M. Markman"
output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: yes
bibliography: references.bib
csl: pnas.csl
figsintext : yes
always_allow_html: true
header-includes:
 \usepackage{float}
---

@@

\newpage
# References

>>>>

---
title: "Supporting Information"
subtitle: "Modeling and leveraging intuitive theories to improve vaccine attitudes"
author: "Derek Powell, Kara Weisman, and Ellen M. Markman"
output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: yes
bibliography: references.bib
csl: science.csl
figsintext : yes
always_allow_html: true
header-includes:
  - \usepackage{float}
  - \usepackage{setspace}\doublespacing
---

@@

\newpage
\singlespace
# References
